Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-11-25 src/tex/ms.tex
potentially final text edits

We count all higher-order companions as secondary, or binary, components. We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour. The lowest metallicity ($\rm{[Fe/H]}=-2.3$) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution with a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.

@@

We consider a fiducial set of assumptions which follow the \cosmic\ defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO). The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass. We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}. We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}. The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}. The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale. Finally, for RLO mass loss which becomes unstable and leads to common envelope evolution (CEE) we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
    \caption{The metallicity-dependent binary fraction for close solar-type binaries with P $< 10^4$ days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations. The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram. The amount of stellar mass formed with super-solar metallicities dominates the distribution. Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale. The opposing trends of these two distributions compete throughout this study.}
    \label{fig:sfh_vs_fb}
    \script{sfh_vs_fb.py}
\end{figure}

The metallicity-dependent close binary fraction for solar-type binaries ($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. The close binary fraction, $f_{\rm{b}}$, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

@@

If the DWD formation time is less than the age of the star particle, we evolve the DWD over the remaining time between its formation and star particle age, $t_{\rm{evol}}$, to produce the present-day population. Once a DWD is formed, we assume that the binary evolves only due to the emission of GWs. Due to tidal effects and mass transfer between their progenitor binaries, all DWDs in our simulations are circular, thus eccentricity does not need to be considered. The orbital evolution over the time $t_{\rm{evol}}$ is then simply defined according to \citet{Peters1964} as
\begin{equation}
    a_f = (a_i - 4\beta t_\text{evol})^{1/4},
\end{equation}
where $a_i$ is the DWD separation at formation, and 
\begin{equation}
    \beta = \frac{64G^3}{5c^5} M_1M_2(M_1+M_2)
\end{equation}
is constant throughout DWD evolution \citep{Peters1964}.

@@

He WDs are unable to form through single star evolution within the lifetime of the Milky Way. Instead, they originate through interactions in close binary systems or binaries with large eccentricities. Because of this, He WDs are able to form with low component masses on order $\sim 0.1\,M_\odot$, with the majority of He WDs in our simulations having masses between 0.2-0.5 $M_\odot$. He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs. The two progenitor stars generally have masses $\lesssim 3\,M_\odot$ which is lower than the progenitors of other DWD types. Our simulated He + He DWDs have an approximately constant distribution of formation times $\gtrsim 2.5\,\rm{Gyr}$. Lastly, since the ZAMS separations are skewed towards shorter values, we also see that the resulting DWD separations are smaller on average than that of other DWD types.

@@

\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS. This changes the timescales of RLO: low-metallicity stars tend to fill their Roche lobes while still on the MS, meaning mass transfer can remain stable which serves to widen the binary. In contrast, high-metallicity systems initiate mass transfer after the donor has left the main sequence, so the binary is more likely to enter a CE phase. Moreover, high-metallicity progenitors tend to have deeper convective envelopes such that a larger fraction of their mass is contained in the envelope relative to lower-metallicity counterparts of the same mass \citep{Amard2019, Amard2020}. When these systems enter a CE phase, it thus requires more orbital energy to eject the CE than for a low-metallicity star at the same point in its evolution, causing a large amount of orbital shrinking. These effects often leads{\sout{s}} to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
    \caption{Average interaction separation, $\overline{a}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50. Solid lines show the average separation at the first RLO for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts. The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains \textbf{304} systems, of which the majority stem from a single low-separation system which was sampled \textbf{258} times times during the simulation. The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin.} 
    \label{fig:CEsep}
    \script{CEsep.py}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
    \caption{The number of LISA-band systems formed for each DWD type and parameter variation as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent close binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, which drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$. There is a double peak in the fiducial and $\alpha25$ He + He populations; the first peak is caused by the sharp drop in formation efficiency past $Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
    \script{lisa_nums.py}
\end{figure*}

All systems that end up radiating GWs in the LISA band have undergone at least one phase of CE evolution. For systems which experience a stable RLO mass transfer in the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.

@@

Of particular interest in variation $q3$ is the CO + He systems. For all of the $q3$ CO + He binaries that reside in the LISA band at present, the He WD unexpectedly forms first through stable mass transfer, with the CO WD forming second through a CE. These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He separation at CE onset. There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above. We also see that the average interaction separation are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/PSD.pdf}
    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of \textbf{$20$} for plotting purposes. Each panel shows a different parameter variation. The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue. The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion). A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of $2$ for the $\alpha5$ and $q3$ parameter variations. This produces a lower GW confusion foreground for frequencies with f$_{\rm{GW}}\leq\sim10^{-3}$ Hz. In contrast, the fiducial and $\alpha25$ parameter variations show very similar confusion foregrounds.}
    \label{fig:PSD}
    \script{PSD.py}
\end{figure*}

@@

The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ when summed over all DWD types. This is due to the log-uniform P$_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$. This tail is less likely to survive to the LISA band at present for the fiducial and $\alpha25$ variations due to the increased propensity for mergers of DWD progenitors. This effect produces an equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations. Although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE star particle metallicity distribution as well as the tendency for the shortest-period DWD progenitors in model F50 to merge, essentially washing out all differences between the populations.

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
    \caption{The chirp mass vs distance for each DWD type is shown for our fiducial parameter variation. Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude. Each panel shows one DWD type, summed over all metallicities. Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction, and a reduction in the height of the DWD Galactic foreground the distributions are very similar.}
    \label{fig:Mc_vs_dist}
    \script{Mc_vs_dist.py}
\end{figure*}

A change in the number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe. We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}. We downsample the PSD frequencies by a factor of 10 for plotting purposes. While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 for parameter variations $\alpha5$ and $q3$. This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ. The foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50.

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation. For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the the entire population for each model in grey. Plots for our three parameter variations \textbf{and discussion on the impact of each varation on the resolved populations} can be found in Appendix \ref{appendix:ASD_vars}. Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower-mass progenitors overflow their Roche lobes at closer separations relative to the higher-mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

The distance and chirp mass of DWDs which exhibit observable orbital evolution due to the emission of GWs during the LISA mission can be measured. This is because the chirp mass -- distance degeneracy in the observed strain can be broken with the observed GW frequency evolution, or chirp. Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured. Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population for the fiducial variation. The same figure for our other three parameter variations is shown in Appendix \ref{appendix:Mc_dist_vars}. The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed). Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.

@@

In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations. These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky-Way-like galaxies. We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ \textbf{with respect to the fiducial case}. This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present. Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced. This is because of the highly inefficient use of orbital energy to eject the common envelope, \textbf{which produces} more stellar mergers, or closer binaries which are more prone to future mergers.

Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This is illustrated in Figure \ref{fig:model_comp}. The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and dotted lines show F50 models. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation. The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two. This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model. \textbf{We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree. This is because an absence of fewer competing GW signals from DWDs in the LISA frequency band leads to individually resolved DWDs. See Appendix \ref{appendix:ASD_vars} for more details.}

@@

An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals. While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of $26\%$ for the former, and surprisingly only by 1\% for the latter. These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs. An increase in resolution capability from the reduced confusion foreground can be extended to other Galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds. Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two depending on the chosen binary evolution model.

>>>>

We count all higher-order companions as secondary (i.e. binary) components. We show curves for all 15 of our metallicity bins, increasing in metallicity from darkest to lightest curve colour. The lowest metallicity ($\rm{[Fe/H]}=-2.3$) shows the highest propensity for short-period binaries, in contrast to higher metallicity systems which have a frequency distribution with a relatively constant companion frequency for orbital periods between $10^4$ and $10^6$ days.

@@

We consider a fiducial set of assumptions which follow the \cosmic\ defaults described in \citet{Breivik2020a} except for the treatment of Roche-lobe overflow (RLO). The stability of RLO mass transfer is determined using critical mass ratios resulting from radius-mass exponents \citep{Webbink1985, Hurley2002}, where the critical mass ratio is defined as the ratio of the donor to accretor mass. We assume critical mass ratios following \citet{Claeys2014} which reduce the standard critical mass ratio assumptions from \citet{Hurley2002} for main sequence (MS) donors by $\sim50\%$ from $3$ to $1.6$ based on the models of \citet{deMink2007} and treat WD accretors separately following the models of \citet{Soberman1997}. We increase the mass loss rate from the donor following Equation 11 of \citet{Claeys2014}. The amount of mass lost during RLO from the donor is limited by the overflow factor of the donor radius to its Roche radius following \citet{Hurley2002}. The amount of mass accepted by the accretor is limited to $10$ times the accretor's mass divided by the accretor's thermal timescale. Finally, for RLO mass loss which becomes unstable and leads to common envelope \textbf{(CE)} evolution we assume that the donor's binding energy is calculated according to the fits detailed in Appendix B of \citet{Claeys2014} and that orbital energy is deposited with $100\%$ efficiency into unbinding the common envelope ($\alpha=1$).

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/sfh_vs_fb.pdf}
    \caption{The metallicity-dependent binary fraction for close solar-type binaries with \textbf{$P_{\rm{orb}}< 10^4$} days (black) plotted against the logarithm of $Z/Z_\odot$, with scatter points denoting the location of the metallicity grid used in our \cosmic\ simulations. The secondary axis shows the amount of mass in stars formed within each metallicity bin from galaxy \textbf{m12i} of the ``Latte" suite in the FIRE-2 simulations as a red histogram. The amount of stellar mass formed with super-solar metallicities dominates the distribution. Note that the primary axis shows $f_{\rm{b}}(Z)$ in linear scale, and the secondary axis shows amount of mass formed in log-scale. The opposing trends of these two distributions compete throughout this study.}
    \label{fig:sfh_vs_fb}
    \script{sfh_vs_fb.py}
\end{figure}

The metallicity-dependent close binary fraction for solar-type binaries ($P_{\rm{orb}} < 10^4$ days), or simply the close binary fraction from here on, is shown in black in Figure \ref{fig:sfh_vs_fb} along with the mass in star particles from galaxy \textbf{m12i}, shown in red, as a function of our metallicity grid. The close binary fraction, \textbf{$f_{\rm{b}}(Z)$}, drops drastically across metallicity while the mass formed in \textbf{m12i} increases significantly. These two opposing trends compete throughout this study along with the impact of metallicity on single star evolution to form the final numerical distribution of systems in our DWD populations.

@@

If the DWD formation time is less than the age of the star particle, we evolve the DWD over the remaining time between its formation and star particle age, $t_{\rm{evol}}$, to produce the present-day population. Once a DWD is formed, we assume that the binary evolves only due to the emission of GWs. Due to tidal effects and mass transfer between their progenitor binaries, all DWDs in our simulations are circular, thus eccentricity does not need to be considered. The orbital evolution over the time $t_{\rm{evol}}$ is then simply defined according to \citet{Peters1964} as
\begin{equation}
    a_f = (a_i - 4\beta t_\text{evol})^{1/4},
\end{equation}
where $a_i$ \textbf{and $a_f$ are} the DWD separations at formation\textbf{ and present day respectively}, and 
\begin{equation}
    \beta = \frac{64G^3}{5c^5} M_1M_2(M_1+M_2)
\end{equation}
is constant throughout DWD evolution \citep{Peters1964}.

@@

He WDs are unable to form through single star evolution within the lifetime of the Milky Way. Instead, they originate through interactions in close binary systems or binaries with large eccentricities. Because of this, He WDs are able to form with low component masses on order $\sim 0.1\,M_\odot$, with the majority of He WDs in our simulations having masses between $0.2$--$0.5$ $M_\odot$. He + He DWDs form through evolution of close binary systems, during which their envelopes are both stripped through RLO and CE phase interactions before Helium ignition occurs. The two progenitor stars generally have masses $\lesssim 3\,M_\odot$ which is lower than the progenitors of other DWD types. Our simulated He + He DWDs have an approximately constant distribution of formation times $\gtrsim 2.5\,\rm{Gyr}$. Lastly, since the ZAMS separations are skewed towards shorter values, we also see that the resulting DWD separations are smaller on average than that of other DWD types.

@@

\textbf{In our \cosmic\ models, lower-metallicity stars evolve faster than high-metallicity stars and have larger radii near the end of the MS. This changes the timescales of RLO: low-metallicity stars tend to fill their Roche lobes while still on the MS, meaning mass transfer can remain stable which serves to widen the binary. In contrast, high-metallicity systems initiate mass transfer after the donor has left the main sequence, so the binary is more likely to enter a CE phase. Moreover, high-metallicity progenitors tend to have deeper convective envelopes such that a larger fraction of their mass is contained in the envelope relative to lower-metallicity counterparts of the same mass \citep{Amard2019, Amard2020}. When these systems enter a CE phase, it thus requires more orbital energy to eject the CE than for a low-metallicity star at the same point in its evolution, causing a large amount of orbital shrinking. These effects often lead to a stellar merger at higher metallicities for a system that would have survived the CE phase at a lower metallicity, thus causing a decrease in formation efficiency with metallicity.}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/CEsep.pdf}
    \caption{Average interaction separation, $\overline{a}_{\rm{CE}}$ of progenitors of close DWDs across metallicity for each DWD type and variation from model F50. Solid lines show the average separation at the first \textbf{CE} for binaries in each metallicity bin. The shaded regions show the $1\sigma$ spread around the mean within each metallicity bin. The average interaction separation increases with metallicity for every DWD type, except for $\alpha5$ which remains approximately constant for CO + He and ONe + X. The positive trend in the average interaction separation is a direct consequence of larger envelope masses of higher-metallicity donors which are less evolved than their lower-metallicity counterparts. The sharp drop of the CO + CO average at the highest-metallicity bin of the fiducial variation is due to binning effects of the figure: it only contains \textbf{304} systems, of which the majority stem from a single low-separation system which was sampled \textbf{258} times times during the simulation. The regions of metallicity where there is not shading beyond the mean trend are also due to low numbers of DWDs in each bin.} 
    \label{fig:CEsep}
    \script{CEsep.py}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/lisa_nums.pdf}
    \caption{The number of LISA-band systems formed for each DWD type and parameter variation as a function of the base-10 logarithm of metallicity, normalized to solar value. The solid line shows the FZ population with a metallicity-dependent close binary fraction incorporated, and the dashed line shows the F50 population for a standard binary fraction of 0.5. The LISA population of DWDs is dominated by stars with super-solar metallicities. This is true even for model FZ, \textbf{where $f_{\rm{b}}(Z)$} drops off significantly for higher metallicities, because of the large number of stars formed in \textbf{m12i} beyond $Z\simeq Z_\odot$. There is a double peak in the fiducial and $\alpha25$ He + He populations; the first peak is caused by the sharp drop in formation efficiency past $Z\simeq0.1\,Z_\odot$ which is then greatly overcompensated for by the amount of star formation at higher metallicities which forms the second peak.}
    \label{fig:lisa_nums}
    \script{lisa_nums.py}
\end{figure*}

All systems that end up radiating GWs in the LISA band have undergone at least one phase of CE evolution. For systems which experience a stable RLO mass transfer as the first interaction, the CE phase plays a key role in shrinking systems with initially wide separations to bring them into the LISA band.

@@

Of particular interest in variation $q3$ is the CO + He systems. For all of the $q3$ CO + He binaries that reside in the LISA band at present, the He WD unexpectedly forms first through stable mass transfer, with the CO WD forming second through a CE. These binaries tend to all have similar resulting orbital separations from mass transfer, as can be seen by the relatively constant curve for CO + He separation at CE onset. There is still a slight increasing trend in CO + He (as well as CO + CO and a more pronounced trend in He + He) for $q3$ that stems from the metallicity-dependent convective envelope discussion above. We also see that the average interaction separations are overall lower for variations $q3$ and $\alpha5$ than for the other two due to the orbital shrinkage that has already occurred from stable mass transfer and the efficient CE phase that will lead to minimal orbital shrinkage respectively.

@@

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/PSD.pdf}
    \caption{The PSD of the entire Galactic DWD GW foreground, summed over all metallicities and DWD types vs GW frequency for models FZ and F50, where the PSD is downsampled by a factor of \textbf{$20$} for plotting purposes. Each panel shows a different parameter variation. The vertical lines show the PSD where model F50 is shown in dark blue and model FZ is shown in light blue. The dashed lines show fits to the rolling boxcar median of width 1000 bins for each PSD (see Section \ref{sec:LISA_obs} for a discussion). A metallicity-dependent binary fraction (model FZ) yields fewer DWDs across all frequencies than a $50\%$ binary fraction (model F50) by roughly a factor of \textbf{two} for the $\alpha5$ and $q3$ parameter variations. This produces a lower GW confusion foreground for frequencies with $f_{\rm{GW}}\lesssim 10^{-3}$ Hz. In contrast, the fiducial and $\alpha25$ parameter variations show very similar confusion foregrounds.}
    \label{fig:PSD}
    \script{PSD.py}
\end{figure*}

@@

The $\alpha5$ and $q3$ variations produce a higher number of F50 systems than FZ when summed over all DWD types. This is due to the log-uniform $P_{\rm{orb}}$ distribution of model F50 having more of the shortest-period binaries than the tails of the log-normal distribution of FZ; a discrepancy which becomes more significant with increasing metallicity as the FZ distribution moves from a peak of log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 3-4$ to log$_{10}$($P_{\rm{orb}}\rm{/day})\simeq 4-6$. This tail is less likely to survive to the LISA band at present for the fiducial and $\alpha25$ variations due to the increased propensity for mergers of DWD progenitors. This effect produces an equal number of systems between FZ and F50 for the fiducial and $\alpha25$ variations. Although the close binary fraction leads to a greater number of low-metallicity systems, this is compensated for by the FIRE star particle metallicity distribution as well as the tendency for the shortest-period DWD progenitors in model F50 to merge, essentially washing out all differences between the populations.

\begin{figure*}
	\includegraphics[width=\textwidth]{figures/Mc_vs_dist_fiducial.pdf}
    \caption{The chirp mass vs distance for each DWD type is shown for our fiducial parameter variation. Only systems with observable evolution in their GW frequency, i.e those which are chirping, and with SNR $>7$, are shown, since these are systems for which distance can be separated from chirp mass within their strain amplitude. Each panel shows one DWD type, summed over all metallicities. Model FZ is indicated with solid light blue contours, and model F50 is indicated with dark blue dashed contours respectively. Contours are shown at the $5^{\rm{th}}$, 25$^{\rm{th}}$, 50$^{\rm{th}}$, 75$^{\rm{th}}$, and 95$^{\rm{th}}$ percentiles. Despite intrinsic changes to population properties induced by a metallicity-dependent binary fraction and a reduction in the height of the DWD Galactic foreground, the distributions are very similar.}
    \label{fig:Mc_vs_dist}
    \script{Mc_vs_dist.py}
\end{figure*}

A change in the number of DWDs in model FZ relative to model F50 is also apparent in the GW PSD LISA will observe. We show the GW PSD of each model, as well as the confusion forground estimate, in Figure~\ref{fig:PSD}. We downsample the PSD frequencies by a factor of \textbf{20} for plotting purposes. While model F50 (dark blue) and model FZ (light blue) produce several thousand large spikes in the PSD across LISA's frequency band, the overall foreground height, including the confusion, is larger for model F50 for parameter variations $\alpha5$ and $q3$. This is a direct consequence of the overall reduction in the size of the close DWD population in model FZ. The foreground height remains unchanged for the fiducial and $\alpha25$ variations when comparing models FZ and F50.

Similar to previous studies, we find that LISA will be able to resolve several thousand DWDs. Figure \ref{fig:LISA_SNR} shows the amplitude spectral density vs GW frequency of the resolved systems with SNR $> 7$ for each DWD type, where the top and bottom rows show results for models FZ and F50 respectively for the fiducial parameter variation. For comparison, we also show the LISA sensitivity curve, including the modeled confusion foreground from each population in black, and the entire population for each model in grey. Plots for our three parameter variations \textbf{and discussion on the impact of each varation on the resolved populations} can be found in Appendix \ref{appendix:ASD_vars}. Apart from each DWD type having a different abundance of resolved systems, the population-wide characteristics remain unchanged between the two binary fraction models. The populations containing at least one He WD occupy the lower-ASD, higher-GW frequency region of parameter space compared to the total population, with CO + He DWDs having larger ASDs than the He + He DWD population. Conversely, DWD types without a He WD component tend to occupy the higher-ASD, lower-GW frequency region of parameter space. This difference is largely due to the formation scenario of DWDs containing a He WD, which form from the ejection of a common envelope created by the He WD progenitor. These lower-mass progenitors overflow their Roche lobes at closer separations relative to the higher-mass progenitors (e.g. Figure~\ref{fig:CEsep}) and thus also produce closer DWDs. While the distance to any one DWD strongly influences its ASD, DWD populations without a He WD component have, on average, higher ASDs due to their more massive WD components.

The distance and chirp mass of DWDs which exhibit observable orbital evolution due to the emission of GWs during the LISA mission can be measured. This is because the chirp mass -- distance degeneracy in the observed strain can be broken with the observed GW frequency evolution, or chirp. Assuming a chirp resolution of $1/T_{\rm{obs}}^2 \sim 8\times10^{-9}\,\rm{Hz}^2$, we select the DWDs whose chirp masses and distances can be measured. Figure \ref{fig:Mc_vs_dist} shows the chirp mass vs the luminosity distance for each DWD type in this selected population for the fiducial variation. The same figure for our other three parameter variations \textbf{and accompanying discussion} is shown in Appendix \ref{appendix:Mc_dist_vars}. The contours show the $5^{\rm{th}}$, $25^{\rm{th}}$, $50^{\rm{th}}$, $75^{\rm{th}}$, and $95^{\rm{th}}$ percentiles for models FZ (light blue) and F50 (dark blue, dashed). Despite the reduction in the height of the confusion foreground when considering model FZ relative to F50, we find that LISA is unable to differentiate between the chirp mass -- distance distributions of the two models.

@@

In each parameter variation, changing the binary evolution assumptions dramatically changes the formation and evolution of the DWD populations. These changes lead to large shifts in the overall number of close DWDs in our synthetic present-day Milky Way-like galaxies. We find that the total number of DWDs with $f_{\rm{GW}}>10^{-4}\,\rm{Hz}$ increases for both variations $q3$ and $\alpha5$ \textbf{with respect to the fiducial case}. This is because there are fewer stellar mergers which occur before the formation of a DWD, thus allowing more systems to evolve due to GW emission and orbit in the LISA frequency band at present. Conversely, for variation $\alpha25$, we find that the number of DWDs orbiting with frequencies in the LISA band is drastically reduced. This is because of the highly inefficient use of orbital energy to eject the common envelope, \textbf{which produces} more stellar mergers, or closer binaries which are more prone to future mergers.

Interestingly, when we compare the populations of each binary fraction model for our variations, we find that the number of close DWDs remains approximately unchanged for our fiducial set of assumptions and $\alpha25$ variation, but is reduced by 50\% for variations $\alpha5$ and $q3$. This is illustrated in Figure \ref{fig:model_comp}. The top panel shows the confusion foreground fits for each binary evolution variation (different colored lines) and for each binary fraction model where the solid lines show FZ models and \textbf{dashed} lines show F50 models. The bottom panel shows the ratio of the number of DWDs orbiting in the LISA frequency band for the FZ models vs the F50 models for each variation. The number of DWDs in the LISA band spans over two orders of magnitude, \textbf{but} the ratio of FZ to F50, as well as the spectral shape of the confusion fit, is either relatively unchanged or reduced by a factor of approximately two. This suggests that assuming a metallicity-dependent binary fraction may change the size of the Galactic close DWD population by a factor of $\sim$ two and the strength of the Galactic DWD GW foreground for LISA depending on the chosen binary evolution model. \textbf{We highlight, however, that for variations where the height of the confusion foreground is reduced, the number of resolved sources is not reduced to an equal degree. This is because fewer competing GW signals from DWDs in the LISA frequency band leads to more individually resolved DWDs. See Appendix \ref{appendix:ASD_vars} for more details.}

@@

An important consequence of a lower Galactic DWD confusion foreground is that relative to the total DWD population, more DWDs can be individually resolved because of the reduction in competing GW signals. While the number of DWDs radiating GWs in the LISA frequency band is reduced by a factor of two for model FZ relative to model F50 for variations $\alpha25$ and $q3$, the number of resolved sources is less affected with a population-wide reduction of \textbf{$22\%$} for the former, and surprisingly only by \textbf{5\%} for the latter. These results are far-reaching since the strength of the Galactic DWD confusion foreground has direct consequences on the detectability of all other LISA sources with small SNRs. An increase in resolution capability from the reduced confusion foreground can be extended to other Galactic binaries that LISA will observe at these frequencies like those involving neutron stars and stellar-origin black holes, as well as other more exotic GW sources like merging supermassive black holes, extreme mass ratio inspirals, or cosmological GW backgrounds. Based on our results, we suggest that studies which employ fits to the confusion foreground based on population synthesis results consider reducing the strength of the Galactic foreground PSD by a factor of two depending on the chosen binary evolution model.
